RNA-seq from 4 cell populations

### 2021-07-30 deconvolution/fans4/molec_profiling.Rmd
bug fix

ggplot(df_deCount, aes(CT1, CT2, fill=count)) + geom_tile() + theme_bw(15) + theme(aspect.ratio=1, plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + scale_fill_gradient(low="white", high="red", limits=c(0, 30000)) + geom_text(aes(label=format(count, big.mark=','))) + xlab('') + ylab('') + ggtitle("Count differentiall expression genes")

@@

ggplot(df, aes(CellType, value, fill=CellType)) + geom_boxplot() + theme_bw(15) + theme(aspect.ratio=1, plot.title = element_text(hjust = 0.5), legend.position = "none") + scale_fill_manual("Cell Type", values=colorCodes) + facet_wrap(~SYMBOL, ncol=5) + ylab(bquote(log[2]~CPM))
```

>>>>

df_deCount$CT1 = factor(df_deCount$CT1, levels(info$CellType))
df_deCount$CT2 = factor(df_deCount$CT2, levels(info$CellType))

ggplot(df_deCount, aes(CT1, CT2, fill=count)) + geom_tile() + theme_bw(15) + theme(aspect.ratio=1, plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + scale_fill_gradient(low="white", high="red", limits=c(0, 30000)) + geom_text(aes(label=format(count, big.mark=','))) + xlab('') + ylab('') + ggtitle("Count differential expression genes")

@@

ggplot(df, aes(CellType, value, fill=CellType)) + geom_boxplot() + theme_bw(15) + theme(aspect.ratio=1, plot.title = element_text(hjust = 0.5), legend.position = "none", axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + scale_fill_manual("Cell Type", values=colorCodes) + facet_wrap(~SYMBOL, ncol=5) + ylab(bquote(log[2]~CPM)) 
```
